\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex
Small tweaks in YM.

The loop momentum structure of ZM theory provides one final hint for
simplifying the pion numerators.  A generic term in the ZM numerator
(of either basis graph) looks schematically like
\begin{equation}
\label{eq:ZMLoopPowCount}
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
\end{equation}
whereas a generic set of local, cubic Feynman rules could have
produced terms with up to $m+n=12$ powers of loop momenta.  When the
pion numerator is forced to have the loop power counting structure in
\cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
freedom parameters reduces to 58.  The pion numerator appearing in the
ancillary files makes exactly this choice. \ace{Is this actually where we
  want this particular footnote to appear?}

@@

\jm{Rather than quoting the number of parameters in the BDN ansatz, I
  would prefer to just focus on what we did since it's more general.
  I don't want it to sound like we just patched a minor hole in their
  argument when I think you've done something much cooler by
  pinpointing the failure to the bowtie graph. I know you put time and
  effort into analyzing the BDN ansatz but I'm worried that the more
  we talk about it, the more it will overshadow the real success
  here.}

Given the close ties between pion and gluon scattering for trees and
at one loop, the existence of the two-loop pion numerator prompts us
to investigate the most general local numerator for YM, without any of
the loop power counting assumptions of Ref.~\cite{Bern:2015ooa}.  We
follow the same general procedure as in \cref{sec:pions}, again
identifying the double-box (2box) and penta-triangle (pt) as the
Jacobi basis graphs and building a the most general ansatz for each of
their numerators compatible with the assumptions in
\cref{sec:bootstrap}.  Because we are now considering pure
Yang-Mills, each monomial in the local ansatz must consist of five
Lorentz scalar dot product s instead of the six for NLSM, and each
monomial must be linear in each of the four external gluon
polarizations.  Thus, the numerator ansatz for both diagrams will be
built from terms of the form:
\begin{equation}
  \mathcal{N}^{\text{YM}}\left[\NLSMBasisDoubleBox \right]\text{ and }\mathcal{N}^{\text{YM}}\left[\NLSMBasisPentaTriangle \right]\in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
  \label{eq:ym-basis}
\end{equation}
where the $k_i$ take the same definition as described near
\cref{eq:scalar-basis}.  In our labeling of the two loop Jacobi-basis
diagrams, shown in \cref{eq:jacobi-basis}, we find that the power
counting bound proposed by Bern, Davies, and Nohle leads to an initial
ansatz with 10,000 terms in the double-box, and 9849 terms for the
penta-triangle.  Without power counting restrictions, both the
double-box and the penta-triangle ansatz have an ansatz with 10,010
terms each.  Imposing diagram automorphisms and maximal-cut gauge
invariance on the two basis diagrams, we reduce the number of terms to
XX for the double-box, and YY for the penta-triangle.  In
Ref.~\cite{Bern:2015ooa}, the unitarity matching constraints were
imposed using a spanning set of minimal physical cuts, shown in
\cref{fig:ym-spanning}.  Instead of also directly going to the
spanning cuts, we work within the framework of the Method of Maximal
Cuts \cite{Bern:2007ct} in order to identify the simplest cut that is in
tension with the kinematic Jacobi relations.

>>>>

The loop momentum structure of ZM theory provides one final hint for
simplifying the pion numerators.  A generic term in the ZM numerator
(of either basis graph) looks schematically like
\begin{equation}
\label{eq:ZMLoopPowCount}
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
\end{equation}
whereas a generic set of local, cubic Feynman rules could have
produced terms with up to $m+n=12$ powers of loop momenta.  When the
pion numerator is forced to have the loop power counting structure in
\cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge
freedom parameters reduces to 58.  The pion numerator appearing in the
ancillary files makes exactly this choice.

@@

Given the close ties between pion and gluon scattering for trees and
at one loop, the existence of the two-loop pion numerator prompts us
to investigate the most general local numerator for YM, without any of
the loop power counting assumptions of Ref.~\cite{Bern:2015ooa}.  We
follow the same general procedure as in \cref{sec:pions}, again
identifying the double-box and penta-triangle as the
Jacobi basis graphs and building a the most general ansatz for each of
their numerators compatible with the assumptions in
\cref{sec:bootstrap}.  Because we are now considering pure
Yang-Mills, each monomial in the local ansatz must consist of five
Lorentz scalar dot product s instead of the six for NLSM, and each
monomial must be linear in each of the four external gluon
polarizations.  Thus, the numerator ansatz for both diagrams will be
built from terms of the form:
\begin{equation}
  \mathcal{N}^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
  \text{ and }
  \mathcal{N}^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
  \in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
  \label{eq:ym-basis}
\end{equation}
where the $k_i$ take the same definition as described near
\cref{eq:scalar-basis}.  In our labeling of the two loop Jacobi-basis
diagrams, shown in \cref{eq:jacobi-basis}, we find that the power
counting bound proposed by Bern, Davies, and Nohle leads to an initial
ansatz with 10,000 terms in the double-box, and 9849 terms for the
penta-triangle.  Without power counting restrictions, both the
double-box and the penta-triangle ansatz have an ansatz with 10,010
terms each.  Imposing diagram automorphisms and maximal-cut gauge
invariance on the two basis diagrams, we reduce the number of terms to
XX for the double-box, and YY for the penta-triangle.  In
Ref.~\cite{Bern:2015ooa}, the unitarity matching constraints were
imposed using a spanning set of minimal physical cuts, shown in
\cref{fig:ym-spanning}.  Instead of also directly going to the
spanning cuts, we work within the framework of the Method of Maximal
Cuts \cite{Bern:2007ct} in order to identify the simplest cut that is in
tension with the kinematic Jacobi relations.
